README.md

### 2022-02-14 README.Rmd
volume and pages
zenodo link

@@

> Fernández-Pascual E, Vaz M, Morais B, Reiné R, Ascaso J, Afif Khouri E, Carta A. [Seed germination ecology of European mesic meadows.](https://dx.doi.org/10.1093/aob/mcab135) *Annals of Botany*, in press.

>>>>

[![DOI](https://zenodo.org/badge/349511614.svg)](https://doi.org/10.5281/zenodo.5602741)

@@

> Fernández-Pascual E, Vaz M, Morais B, Reiné R, Ascaso J, Afif Khouri E, Carta A. [Seed ecology of European mesic meadows.](https://dx.doi.org/10.1093/aob/mcab135) *Annals of Botany* 129, 121-133.
